### 2016-02-19 Projects/DelCo_2014_2015/Reports/FDS_Validation_Report/TeX_Files/FDS_Exp_Description_Report.tex
Added content to instrumentation section of FDS valid. report

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{..//Figures/Floor_Plans/West_Structure_2nd_Floor_Dimensioned_Full}
	\\~\\
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Dimensioned_Full}
	\caption[Dimensioned floor plan of the first and second floors of the West Structure.]{Dimensioned floor plan of the second floor (top) and first floor (bottom) of the West Structure.}
	\label{fig:west_dimensioned_plan}
\end{figure}
% make new 1st floor plan with rear door completely sealed off

@@

\section{Instrumentation}
\label{sec:Instrumentation}

\subsection{East Structure}
\label{sec:East_instrument}

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Dimensioned_Instrumentation}
	\caption[Dimensioned floor plan of the East Structure.]{East Structure floor layout.}
	\label{fig:east_instrumentation}
\end{figure}

\subsection{West Structure}
\label{sec:West_instruments}

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Dimensioned_Instrumentation}
	\\~\\
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Dimensioned_Instrumentation}
	\caption[Dimensioned floor plan of the first and second floors of the West Structure.]{Dimensioned floor plan of the second floor (top) and first floor (bottom) of the West Structure.}
	\label{fig:west_instrumentation}
\end{figure}

@@

\section{Propane Burners}
\label{sec:Burners}
Three propane burners, each with a 0.6 m X 0.6 m square opening 0.14 m above the floor, were used as the fuel source in every experiment described in this report. Propane flowed at a known volumetric flow rate during the experiments.

>>>>

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{..//Figures/Floor_Plans/West_Structure_2nd_Floor_Dimensioned_Full}
	\\~\\
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Dimensioned_Full}
	\caption[Dimensioned floor plans of the West Structure.]{Dimensioned floor plan of the second floor (top) and first floor (bottom) of the West Structure.}
	\label{fig:west_dimensioned_plan}
\end{figure}
% make new 1st floor plan with rear door completely sealed off

@@

\section{Instrumentation}
\label{sec:Instrumentation}
The structures were instrumented for temperature, gas velocity, heat flux, and gas concentration measurements. Gas temperatures in the burn rooms were measured with bare-bead, Chromel-Alumel (type K) thermocouples. Additional single thermocouples were installed in conjunction with the bi-directional probes for gas velocity measurements. The single thermocouples were bare-bead, Chromel-Alumel (type K) thermocouples, with a 1.0~mm (0.04~in) nominal diameter. The thermocouple wire was protected with an 3.2~mm (0.125~in) diameter inconnel sheath. Schmidt-Boelter gauges were used to measure both total heat flux and radiant heat flux (radiometer). A radiometer is a total heat flux gauge with a zirconium plate to prevent contributions from convective heat transfer. Calibrated pumps pulled gas samples through a sample conditioning system to eliminate moisture in the sample. Then, the dry gas sample was piped to a series of gas analyzers and the concentrations of oxygen, carbon monoxide, and carbon dioxide were measured. A legend, which clarifies the instrumentation schematics discussed in the follow sections, is included in Fig.~\ref{fig:Instrumentation_Legend}.

% \begin{figure}[!ht]
% 	\includegraphics[width=0.35\columnwidth]{../Figures/Floor_Plans/Legend}
% 	\caption[Instrumentation Legend.]{Instrumentation Legend.}
% 	\label{fig:Instrumentation_Legend}
% \end{figure}
% \FloatBarrier

\subsection{East Structure}
\label{sec:East_Instrumentation}
The East Structure was instrumented with 5 bare-bead thermocouple arrays, 4 bi-directional probe plus solid thermocouple arrays, 5 total heat flux plus radiometer sensor pairs, and 2 gas sample inlet pipes at the locations shown in Fig.~\ref{fig:east_instrumentation}.

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Dimensioned_Instrumentation}
	\caption{Location of instrumentation in the East Structure.}
	\label{fig:East_Instrumentation}
\end{figure}

Each bare-bead thermocouple array was composed of 8 thermocouples. The top sensor was 0.03~m (1~in) below the ceiling and the remaining thermocouples were space 0.3~m (1~ft) apart with the bottom thermocouple being 2.13~m (7~ft) below the ceiling. The three bi-directional probe and solid thermocouple arrays located at the exterior doorways of the structure contained 8 probes centered in the doorway with the first probe 0.08~m (0.25~ft) below the soffit and the remaining probes at 0.34~m (1.1~ft), 0.61~m (2~ft), 0.88~m (2.9~ft), 1.15~m (3.7~ft), 1.42~m (4.7~ft), 1.68~m (5.5~ft), and 1.95~m (6.4~ft) below the soffit. The fourth bi-directional probe and solid thermocouple array was located at the roof vent and contained three probes \textit{centered between the east and west sides of the vent and spaced ?? apart between the north and south sides.} The total heat flux guage/radiometer pairs were set to be 0.15~m (0.5~ft) off the ground and aimed to view the ceiling. Gas concentrations were pulled through \textit{3.2~mm (0.125~in) diameter stainless steel tubing located 1.22~m (4~ft) above the floor.}

\subsection{West Structure}
\label{sec:West_Instrumentation}
The first floor of the West Structure was instrumented with 3 bare-bead thermocouple arrays, 3 bi-directional probe plus solid thermocouple arrays, and 1 gas sample inlet pipe, and the second floor was equipped with 3 bare-bead thermocouple arrays, 4 bi-directional probe plus solid thermocouple arrays, and 1 gas sample inlet pipe. The locations of the instrumentation in the West Structure is shown in Fig.~\ref{fig:west_instrumentation}.

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Dimensioned_Instrumentation}
	\\~\\
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Dimensioned_Instrumentation}
	\caption[Location of instrumentation in the West Structure.]{Location of instrumentation in the second floor (top) and first floor (bottom) of the West Structure.}
	\label{fig:west_instrumentation}
\end{figure}

The thermocouples in the bare-bead thermocouple arrays were spaced in the same manner as the arrays in the East Structure. The bi-directional probe and thermocouple arrays contained 8 probes with spacing identical to the arrays at the exterior doors of the East Structure. 3.2~mm (0.125~in) stainless steel tubing was located 1.22~m (4~ft) above the floor and used to pull gas samples from the environment.

\subsection{Propane Burners}
\label{sec:Burners}
Three propane burners, each with a 0.6 m X 0.6 m square opening 0.14 m above the floor, were used as the fuel source in every experiment described in this report. Propane flowed at a known volumetric flow rate during the experiments.

@@
